% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{UMANG TANEJA}

\basicInfo{
  \email{umang.taneja0173@gmail.com} \textperiodcentered\ 
  \phone{(+91) 8750461304} \textperiodcentered\ 
  \linkedin[ugtan]{https://www.linkedin.com/in/ugtan}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Inderprastha Engineering College (IPEC)}, Ghaziabad, India}{2017 -- Present}
\textit{BTech} in Computer Science and Engineering (CSE), expected June 2021

\section{\faUsers\ Work Experience}
\datedsubsection{\textbf{Software Package Data Exchange (SPDX)}}{May 2019 -- Aug 2019}
\role{Student Developer}{Google Summer of Code 2019}
Brief introduction: The project deals with extending the functionality of the license submittal feature where users can submit new license requests to the SPDX’s license-list-XML repository to be further reviewed by the SPDX legal team to check if the license is worthy of adding it to the SPDX License List.
\begin{itemize}
  \item Implemented API for the license submittal feature.
  \item Compare with already submitted licenses as well as rejected licenses.
  \item Check for duplicate and near matches using sorensen dice string matching algorithm.
  \item Improved the XML generating algorithm and XML formatting of the XML editor.
\end{itemize}

\section{Projects}
\begin{itemize}
  \item \textbf{Stock Price Prediction} A project that predicts the prices of stocks using different machine learning algorithms like linear regression, LSTM, Arima, etc and performs sentiment analysis on tweets related to that stock.
  \item \textbf{Fingerprint detection system} Takes fingerprint from the user, process it and extract using SIFT and compares it with the other fingerprints.
  \item \textbf{Covid19 Telegram Bot} A telegram bot to track various covid19 cases around the globe and visualize the data via plots.
  \item \textbf{Virtual Police Station} Developed a virtual police station system for Smart India Hackaton(SIH) to ease the process of filing a FIR online. Successfully cleared SIH Internals.
  \item \textbf{License Matcher} Developed a CLI tool that uses string matching algorithm to check if the license is present on the license list or not.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Python, C, C++, SQL
  \item Platform: Linux
  \item Others: Git, Rest APIs, Docker, Machine learning
\end{itemize}

\section{\faHeartO\ Achievements}
\datedline{\textit{Google Summer of Code 2019}, 5,606 students participated from 103 countries only 1,276 selected}{May. 2019}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item Blog: http://ugtan.me
  \item GitHub: https://github.com/ugtan
  \item Languages: English, Hindi - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
